Geospatial - Assignment 2

### 2025-02-04 hw2/hw2_MoritzPeistNoemiLucchiSimonVellin.Rmd
Spelling mistakes Ex 2 checked

# Exercise 2: Porteuos data

@@

```{r}
# We isolate the African airports from our global data sets to stay efficient.
sf.africa <- sf.world %>%
  filter(REGION_UN == "Africa") %>%
  filter(!st_is_valid(.)) %>%
  st_make_valid()

@@

# Data Wrangling - st_distance() returns a matrix with one row per market and one column per coast segment.

>>>>

# Exercise 2: Porteous data

@@

```{r}
# We isolate the African airports from our global data sets to stay efficient
sf.africa <- sf.world %>%
  filter(REGION_UN == "Africa") %>%
  filter(!st_is_valid(.)) %>%
  st_make_valid()

@@

# Data Wrangling - st_distance() returns a matrix with one row per market and one column per coast segment
